MCC Models

### 2019-03-11 papers/full_paper/models.Rmd
update model description

```{r model parameter adults}
speakOptParam <- '
var data = dataFromR.data

@@

```{r model parameters children}
childModelParam <- '
var prefData = dataFromR.prefData
var infData = dataFromR.infData

@@

ggplot(data = child_prior_plot, aes(x = age_num, y = correct, col = condition)) +
  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
  geom_line(aes(x = age_num, y = model, col = condition), size = 1.5, lty = 2)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_solarized(name = "Condition")+
  scale_fill_solarized(name = "Condition")
```

@@

ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
  geom_line(alpha = .5, size = .7)+
  labs(x="Age",y="Speaker optimality parameter")+
  theme_few() +
  geom_hline(yintercept = 0, lty=2)+
  ylim(-3,3)+
  guides(alpha = F)
```

>>>>

```{r model parameter adults}

# The prior on the speaker optimality parameter is largely positive but also contains negative values so that it could, in theory, result in a parameter that leads to model predictions below chance. The same prior is used for the intercept on children's parameters, where performance was below chance.  
speakOptParam <- '
var data = dataFromR.data

@@

```{r model parameters children}
# In theory, we would expect the speaker optimality parameter to always be positive. The prior for the intercept should therefore not include neagtive values. However, in the context of our study, the youngest children performed below chance and increased with age. This pattern can only be captured by the model if we allow the intercept to take negative values. To combine these considerations, the prior for the intercept is skewed towards being positive, but also includes negative values. The prior on the slope is agnostic about the shape of the developmental trajectory.
childModelParam <- '
var prefData = dataFromR.prefData
var infData = dataFromR.infData

@@

ggplot(data = child_prior_plot, aes(x = age_num, y = correct, col = condition)) +
  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
  geom_smooth(aes(fill = condition),method = "lm", se = T, alpha = .5, size = .7)+
  geom_line(aes(x = age_num, y = model, col = condition), size = 1.5, lty = 2)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_solarized(name = "Condition")+
  scale_fill_solarized(name = "Condition")

# dashed line represents the developmental trajectories based on the estimated parameters 
```

@@

plot_child_so <- ggplot(data = child_so_plot, aes(x = age_num, y = model)) +
  geom_hline(yintercept = 0, lty=2)+
  geom_line( size = 2)+
  labs(x="Age",y="Speaker optimality parameter")+
  theme_few() +
  ggtitle("Speaker optimality parameter")+
  ylim(-3,3)+
  guides(alpha = F)

plot_ex1_child <-child_ex1_data %>%
  group_by(age_num, id) %>%
  summarise(correct = mean(correct))%>%
  ggplot(data = ., aes(x = age_num, y = correct)) +
  geom_jitter(alpha = 0.5, height = 0.02, width = 0)+
  geom_smooth(method = "lm", se = T, alpha = .5, size = .7)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="Age",y="Proportion Correct")+
  ggtitle("Data ex1 children")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)

ggarrange(plot_child_so,plot_ex1_child)
```
